---
title: "SI 618 Homework 7"
author: "CHEN,Po-Heng (pohechen)"
date: "March 9, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(data.table)
```

## Loading and Cleaning Data (5 points)
```{r}
d = read.csv('businessdata.tsv', sep = '\t') 
# I used read.csv to read because it's more robust than read.table
# and when using read.table, it creates error
d = na.omit(d)
summary(d)
d = data.table(d)
```

## Histograms of Star Ratings (10 points)
```{r}
ggplot(d, aes(x = stars, fill = state)) +
    geom_histogram(binwidth = 1, alpha = 0.8) +
    facet_grid(. ~ state)
```

```{r}
ggplot(d, aes(x = stars, fill = state)) +
    geom_histogram(aes(y=..density..), binwidth = 1, alpha = 0.8) +
    facet_grid(. ~ state)
```

## Histograms of Review Counts (10 points)
```{r}
ggplot(d, aes(x = review_count)) +
    geom_histogram(binwidth = 10, alpha = 0.8) +
    ggtitle('Histograms of Review Counts') +
    labs(x = 'Review Counts')
```

```{r}
p = d[d$review_count <= 200, ]
ggplot(p, aes(x = review_count)) +
    geom_histogram(binwidth = 1, alpha = 0.8) +
    ggtitle('Histograms of Review Counts') +
    labs(x = 'Review Counts')
```

## Boxplot of Star Ratings by States (10 points)
```{r}
ggplot(d, aes(x = state, y = stars, col = state, fill = state)) +
    geom_boxplot(alpha = 0.6) +
    ggtitle('Star Ratings by States') +
    labs(x = '')
```

## Jittered Plot of Star Ratings by States (10 points)
```{r}
ggplot(d, aes(x = state, y = stars, col = state, fill = state)) +
    geom_jitter(alpha = 0.6) +
    ggtitle('Star Ratings by States') +
    labs(x = '')
```

## Bar Chart of Number of Businesses by State (10 points)
```{r}
ggplot(d, aes(x = reorder(state, state, function(x)-length(x)))) +
    geom_bar() +
    labs(x = 'State')
```

## Jittered Scatterplot of Stars and Review Counts (10 points
```{r}
ggplot(d, aes(x = stars, y = review_count, col = state, fill = state)) +
    geom_jitter(alpha = 0.6) +
    labs(y = 'Review Count')

```


## Slice and Dice Data using data.table syntax (or plyr)

#### Subsetting Data (10 points)
```{r}
tmp = d[, rank:= rank(-stars, ties.method = 'first'), by = .(city, main_category)]
print(tmp)
```

```{r}
tmp = tmp[rank %in% 1:5 & main_category == 'Chinese', .(city, name, rank, stars) ]
tmp = tmp[order(city, rank),]
print(tmp)
```

## Summarize Data (10 points)
```{r}
tmp = d[, .(m_review = round(mean(review_count))) ,by = .(state)]
tmp = transform(tmp, state = reorder(state, -m_review)) ## magic trick
ggplot(tmp, aes(x = state, y = m_review)) +
    geom_bar(stat = "identity")
```


